Structural replication of nanoporous media using procedural noise

### 2018-11-04 ms.tex
stuff

\subsection{Future work}
We have only considered the simplest kind of procedural noise: a simple sum over modes with
threshold cut-off $\tau$, scale fall-off persistence $\psi$ and initial scale $\nu$. 
We have also seen that, even though both porosity and surface area accurately reproduced,
there are features in the radial distribution function that are not fully captured with the current model. 
This is evident from the images of the simulated structure seen in figure \ref{fig:porous_vs_model},
where the connecting nearly one-atom thin walls are difficult to reproduce with the current model. 
However, as procedural noise exert properties closely related to that of fractals, it is possible
to extend the number of parameters and define new models with very different properties. 
Some examples of these models are depicted in figure \ref{fig:future_models}, where the left- and
centre images show a new model with two new parameters (offset and gain), while the rightmost panel shows a simulation where the scale $\nu$ is itself being perturbed by procedural noise, yielding strong circular asymmetric patterns.

@@

%Minkowski functionals and topology, genus etc

%Swiss noise

\begin{figure*}
\includegraphics[width=1\textwidth]{future_models.png}
\caption{Example of future models. Left panel: A multi-fractal model with thin surfaces and large pores. Centre panel: a multi fractal with cave-like structures. Right panel: A model with strong asymmetric noise. }
\label{fig:future_models}
\end{figure*}

>>>>

\subsection{Future work}
We have only considered the simplest kind of procedural noise: a simple sum over modes with
threshold cut-off $\tau$, scale fall-off persistence $\psi$ and initial scale $\nu$. 
We have also seen that, even though both porosity and surface area accurately reproduced,
there are features in the radial distribution function that are not fully captured with the current model. 
This is evident from the images of the simulated structure seen in figure \ref{fig:porous_vs_model},
where the connecting nearly one-atom thin walls are difficult to reproduce with the current model. 
However, as procedural noise exert properties closely related to that of fractals, it is possible
to extend the number of parameters and define new models with very different properties.

@@
